Exploiting the Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-26 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Fixing bibliography
Fixes biblio again and more comments

\subsection{Collaboration}
\label{sec:col}
After entering the web application by using their Facebook account,
users can collaborate with their Facebook friends, 
sharing those individuals they like, or by taking individuals
from their friend\'s collections by using the web interface depicted 
in Figure \ref{fig:web}.
At the top left corner a list of Facebook friends is presented
to encourage users to interact with the system. In the central 
\emph{ Wall } area, an individual sampled from the population that is
being evolved via the evolutionary algorithm 
is shown to the user.
Here, the user can interact with the system in two ways.
First, he can assign a quality assessment to the individual using
a five star rating measure or
additionally, a user can choose to add an image to one of their \emph{Collections}.
A collection is a special folder to store those individuals a user prefers and wishes
to save. After the user finishes interacting with the individual
on the Wall, he can choose to retrieve a new one from the population.
At the left side, is the \emph{Collections} section.
The user can create several collections, to group and organize his favorite 
artifacts. Moreover, a user can browse the content of each collection and from
there share images through the social network.
When a user browses over an individual a detail pane shows how many users have
liked the individual. The pane also includes a link to the individual's 
details, the parents, genetic operators that created it, and genealogy information.

@@

\begin{itemize}
  \item {\bf Interactive Evolutionary Computational system} 
  This is the real world system that we are going to represent in the model, 
  it consist of human users and their interactions with one or more individuals
  from
  the population. There are many ways in which humans could interact 
  with individuals, this could be through a mobile device, a user interface 
  or by interacting with real world objects generated as part of the algorithm 
  \cite{de2014artists,de2013unplugging}. 
  There is also the possibility that fitness or even part of the search 
  to be done by devices lent by the human \cite{merelo2016performance}.
  The information gathered through the interaction is the primary concern
  as it will guide the search.

@@

\item {\bf Shared} When a user takes an individual from a friends collection, this interactions 
is described by a {\tt share} relationship, between the user and the individual.

@@

Gamification is defined by Deterding et al. as
``the use of game design elements in non-game contexts'' \cite{deterding2011game}.
The gamification element employed in this work is rewarding mechanism 
\cite{dubois2013understanding}, in general they consisting of a reputation systems with score points, 
levels and leader boards. Points are awarded to users in response of
the accomplishment of certain activities that need to be encouraged. Levels depend
on the score and certain features of the game are only available to gamers when 
they reach a giving level.

@@

The link used in the call for participation
was shortened URL, in order to obtain additional data and analytic of the visitors.
In table \ref{tab:urls} the URL for each deployment in the Heroku platform is shown,
along with the short URL and the analytics link. In the same table a link to the GitHub 
application repository used to deploy to Heroku is also listed.

@@

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_2.png}
    \caption{User network view of the Base deployment}
    \label{fig:B-network}
\end{figure}
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_3.png}
    \caption{User network view of the Graph Gamification deployment}
    \label{fig:GG-network}
\end{figure}
\begin{figure*}[!t]
    \centering
        \includegraphics[width=5.5in]{img/comparison.png}
    \caption{Top ranked number individuals rated by user using a
     logarithmic scale.}
    \label{fig:top-ranked-participation}
\end{figure*}

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\bibliographystyle{IEEEtran}
\bibliography{evospace-i,volunteer,biblio}

>>>>

\subsection{Collaboration}
\label{sec:col}
After entering the web application by using their Facebook account,
users can collaborate with their Facebook friends, 
sharing those individuals they like, or by taking individuals
from their friend's collections by using the web interface depicted 
in Figure \ref{fig:web}.
At the top left corner a list of Facebook friends is presented
to encourage users to interact with the system. In the central 
\emph{ Wall } area, an individual sampled from the population that is
being evolved via the evolutionary algorithm 
is shown to the user.
Here, the user can interact with the system in two ways.
First, he can assign a quality assessment to the individual using
a five star rating measure or
additionally, a user can choose to add an image to one of their \emph{Collections}.
A collection is a special folder to store those individuals a user prefers and wishes
to save. After the user finishes interacting with the individual
on the Wall, he can choose to retrieve a new one from the population.
At the left side, is the \emph{Collections} section.
The user can create several collections, to group and organize his favorite 
artifacts. Moreover, a user can browse the content of each collection and from
there share images through the social network.
When a user browses over an individual a detail pane shows how many users have
liked the individual. The pane also includes a link to the individual's 
details, the parents, genetic operators that created it, and genealogy information.

@@

\begin{itemize}
  \item {\bf Interactive Evolutionary Computational system} 
  This is the real world system that we are going to represent in the model, 
  it consist of human users and their interactions with one or more individuals
  from
  the population. There are many ways in which humans could interact 
  with individuals, this could be through a mobile device, a user interface 
  or by interacting with real world objects generated as part of the algorithm 
  \cite{de2014artists,de2013unplugging}. 
  There is also the possibility that fitness or even part of the search 
  to be done by devices lent by the human \cite{DBLP:conf/gecco/MereloCGCRV16}.
  The information gathered through the interaction is the primary concern
  as it will guide the search.

@@

\item {\bf Shared} When a user takes an individual from a friend's collection, this interactions 
is described by a {\tt share} relationship, between the user and the individual.

@@

%This section on gamification should go to the intro and state of the
%art, since it is one of the main points of the paper - JJ
Gamification is defined by Deterding et al. as
``the use of game design elements in non-game contexts'' \cite{deterding2011game}.
The gamification element employed in this work is rewarding mechanism 
\cite{dubois2013understanding}, in general they consisting of a reputation systems with score points, 
levels and leader boards. Points are awarded to users in response of
the accomplishment of certain activities that need to be encouraged. Levels depend
on the score and certain features of the game are only available to gamers when 
they reach a giving level.

@@

The link used in the call for participation
was shortened Google URL, that provides metadata and analytics for the
users that click on it. 
In table \ref{tab:urls} the URL for each deployment in the Heroku platform is shown,
along with the short URL and the analytics link. In the same table a link to the GitHub 
application repository used to deploy to Heroku is also listed.    
%Isn't this anonymous? - JJ

@@

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_2.png}
    \caption{User network view of the Base deployment}
    \label{fig:B-network}
\end{figure}
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_3.png}
    \caption{User network view of the Graph Gamification deployment}
    \label{fig:GG-network}
\end{figure}
\begin{figure*}[!t]
    \centering
        \includegraphics[width=5.5in]{img/comparison.png}
    \caption{Top ranked number individuals rated by each user using a
     logarithmic scale.} % Explain a little more and label axes. The
                         % three lines have the same label,
                         % "participation". Not too clear - JJ
    \label{fig:top-ranked-participation}
\end{figure*}

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\bibliographystyle{IEEEtran}
\bibliography{evospace-i,volunteer,biblio,geneura}
